KidsAIR: initial exposure analysis

### 2020-04-03 ambient_initial.Rmd
analysis updates

---
title: "KidsAIR: ambient data"
author: "Ethan Walker"
date: "Started 30 March 2020, Updated 30 March 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(ggmap)
library(maps)
library(tigris)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

@@

# Mapping zipcodes, weather stations, pm stations - WMT
# These steps are repeated for NN and AK below
```{r}
# Zipcodes for each KidsAIR study home were downloaded from the server
# If there was no zipcode provided, the zipcode from the nearest town was used
# Here, WMT zipcodes are joined with the US zipcode data
# This step gives lat/long coordinates for each WMT zipcode
wmt_zipcodes_new <- wmt_zipcodes %>% 
  left_join(us_zipcodes, by = "zip") %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  mutate(lat_zip = lat,
         long_zip = long)

@@

# Here, zipcodes and weather stations are plotted on a map
# Colors match for weather stations and zips that are closest together
wmt_plot <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=wmt_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 3) +
    geom_point(data=wmt_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "WMT zipcodes and weather stations") +
    scale_color_manual(values = jv_palette)
wmt_plot

@@

# PM monitors and zipcodes are plotted below
# Colors match for PM monitors and zips that are closest together
wmt_plot <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=wmt_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 3) +
    geom_point(data=wmt_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "WMT zipcodes and PM monitors") +
    scale_color_manual(values = jv_palette)
wmt_plot
```

# Mapping zipcodes, weather stations, pm stations - NN
```{r}
nn_zipcodes_new <- nn_zipcodes %>% 
  left_join(us_zipcodes, by = "zip") %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  mutate(lat_zip = lat,
         long_zip = long)

@@

nn_plot_temp_stations <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=nn_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 3) +
    geom_point(data=nn_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "NN zipcodes and weather stations") +
    scale_color_manual(values = jv_palette)
nn_plot_temp_stations

@@

nn_plot <- nn_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=nn_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 3) +
    geom_point(data=nn_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "NN zipcodes and PM monitors") +
    scale_color_manual(values = jv_palette)
nn_plot
```

# Mapping zipcodes, weather stations, pm stations - WMT
```{r}
ak_zipcodes_new <- ak_zipcodes %>% 
  left_join(us_zipcodes, by = "zip") %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  mutate(lat_zip = lat,
         long_zip = long)

@@

zipcodes_map <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=ak_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 3) +
    geom_point(data=ak_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "AK zipcodes and weather stations") +
    scale_color_manual(values = jv_palette) 
zipcodes_map

@@

ak_plot <- ak_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=ak_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 3) +
    geom_point(data=ak_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "AK zipcodes and PM monitors") +
    scale_color_manual(values = jv_palette)
ak_plot
```

# Compile temperature data and filter for closest stations
```{r}
# Read in ambient weather files and bind together
list_files <- list.files("Input/ambient/temp_data")
# Set working directory and load files in list; extract file name and add as column
## run next 10 lines together
setwd("Input/ambient/temp_data") # set new working directory
initial_data = tibble(file_name = list_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv, 
                            col_names = c("station", "wban", "temp_date",
                                          "mean_temp", "t1", "mean_dewp", "t2",
                                          "t3", "t4", "mean_pressure", "t5",
                                          "mean_visib_miles", "t6", "mean_wind_knots",
                                          "t7", "max_wind_knots", "t8", "max_temp",
                                          "min_temp", "precip", "snow_depth", "t9"))) %>%
  unnest(save_data)

@@

# Compile PM data and filter for correct dates/variables
```{r}
pm_stations <- read_xlsx("Input/ambient/pm_station_list.xlsx")

@@

# Add new variables to pm/temp datasets
```{r}
kids_amb_pm_data <- read_rds("Output/kids_amb_pm_data.rds")
kids_temp_data <- read_rds("Output/kids_temp_data.rds")

>>>>

---
title: "KidsAIR: ambient data"
author: "Ethan Walker"
date: "Started 30 March 2020, Updated 3 April 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, 
                      include = TRUE, warning = FALSE, message = FALSE,
                      fig.height = 6, fig.width = 8)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(ggmap)
library(maps)
library(tigris)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", 
               "#0072B2", "#D55E00", "#CC79A7")
```

@@

```{r}
# Mapping zipcodes, weather stations, pm stations - WMT
# These steps are repeated for NN and AK below

# Zipcodes for each KidsAIR study home were downloaded from the server
# If there was no zipcode provided, the zipcode from the nearest town was used
# Here, WMT zipcodes are joined with the US zipcode data
# This step gives lat/long coordinates for each WMT zipcode
wmt_zipcodes_new <- wmt_zipcodes %>% 
  left_join(us_zipcodes, by = "zip") %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  mutate(lat_zip = lat,
         long_zip = long)

@@

# Here, zipcodes and weather stations are plotted on a map
# Colors match for weather stations and zips that are closest together
wmt_plot <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "azure", size = 1.2) +
    geom_point(data=wmt_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 3) +
    geom_point(data=wmt_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "WMT zipcodes and weather stations", color = "Weather station") +
    scale_color_manual(values = cbPalette)
wmt_plot

@@

# PM monitors and zipcodes are plotted below
# Colors match for PM monitors and zips that are closest together
wmt_plot <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "azure", size = 1.2) +
    geom_point(data=wmt_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 3) +
    geom_point(data=wmt_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "WMT zipcodes and PM monitors", color = "EPA Monitor") +
    scale_color_manual(values = cbPalette)
wmt_plot
```

```{r}
# Mapping zipcodes, weather stations, pm stations - NN

nn_zipcodes_new <- nn_zipcodes %>% 
  left_join(us_zipcodes, by = "zip") %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  mutate(lat_zip = lat,
         long_zip = long)

@@

nn_plot_temp_stations <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "azure", size = 1.2) +
    geom_point(data=nn_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 3) +
    geom_point(data=nn_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "NN zipcodes and weather stations", color = "Weather station") +
    scale_color_manual(values = cbPalette)
nn_plot_temp_stations

@@

nn_plot <- nn_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "azure", size = 1.2) +
    geom_point(data=nn_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 3) +
    geom_point(data=nn_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "NN zipcodes and PM monitors", color = "EPA monitor") +
    scale_color_manual(values = cbPalette)
nn_plot
```

```{r}
# Mapping zipcodes, weather stations, pm stations - WMT

ak_zipcodes_new <- ak_zipcodes %>% 
  left_join(us_zipcodes, by = "zip") %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  mutate(lat_zip = lat,
         long_zip = long)

@@

zipcodes_map <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "azure", size = 1.2) +
    geom_point(data=ak_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 5) +
    geom_point(data=ak_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 5) +
    theme_void() +
    labs(title = "AK zipcodes and weather stations", color = "Weather station") +
    scale_color_manual(values = cbPalette) 
zipcodes_map

@@

ak_plot <- ak_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "azure", size = 1.2) +
    geom_point(data=ak_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 5) +
    geom_point(data=ak_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 5) +
    theme_void() +
    labs(title = "AK zipcodes and PM monitors", color = "EPA monitor") +
    scale_color_manual(values = cbPalette)
ak_plot
```

```{r, echo=FALSE, include=FALSE, eval=FALSE}
# Compile temperature data and filter for closest stations

# Read in ambient weather files and bind together
list_files <- list.files("Input/ambient/temp_data")
# Set working directory and load files in list; extract file name and add as column
## run next 10 lines together
setwd("Input/ambient/temp_data") # set new working directory
initial_data = tibble(file_name = list_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv, 
                            col_names = c("station", "wban", "temp_date",
                                          "mean_temp", "t1", "mean_dewp", "t2",
                                          "t3", "t4", "mean_pressure", "t5",
                                          "mean_visib_miles", "t6", "mean_wind_knots",
                                          "t7", "max_wind_knots", "t8", "max_temp",
                                          "min_temp", "precip", "snow_depth", "t9"))) %>%
  unnest(save_data)

@@

```{r, echo=FALSE, include=FALSE, eval=FALSE}
# Compile PM data and filter for correct dates/variables

pm_stations <- read_xlsx("Input/ambient/pm_station_list.xlsx")

@@

```{r, echo=FALSE, include=FALSE, eval=FALSE}
# Add new variables to pm/temp datasets

kids_amb_pm_data <- read_rds("Output/kids_amb_pm_data.rds")
kids_temp_data <- read_rds("Output/kids_temp_data.rds")

### 2020-04-03 ambient_summary.Rmd
analysis updates

---
title: "KidsAIR: ambient temperature and PM analysis"
author: "Ethan Walker"
date: "Started 1 April 2020, Updated 1 April 2020"
output: powerpoint_presentation
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(ggmap)
library(maps)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

@@

wmt_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "WMT") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "tan") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    theme_void() +
    labs(title = "WMT mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = EPA monitors") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 8)
wmt_plot
```

```{r}
nn_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "NN") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "tan") +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "NN mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = EPA monitors") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 1.5)
nn_plot
```

```{r}
ak_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "AK") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "tan") +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "AK mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = EPA monitors") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 6)
ak_plot
```

@@

wmt_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "WMT") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "tan") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    theme_void() +
    labs(title = "WMT mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 20)
wmt_plot
```

```{r}
nn_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "NN") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "tan") +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "NN mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 45)
nn_plot
```

```{r}
ak_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "AK") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "tan") +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 5, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "AK mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 30)
ak_plot
```

>>>>

---
title: "KidsAIR: ambient temperature and PM analysis"
author: "Ethan Walker"
date: "Started 1 April 2020, Updated 3 April 2020"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(ggmap)
library(maps)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", 
               "#0072B2", "#D55E00", "#CC79A7")
```

@@

wmt_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "WMT") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    theme_void() +
    labs(title = "WMT mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = EPA monitors",
         fill = "Ambient PM", size = "Ambient PM") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 8)
wmt_plot
```

```{r}
nn_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "NN") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "NN mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = EPA monitors",
         fill = "Ambient PM", size = "Ambient PM") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 1.5)
nn_plot
```

```{r}
ak_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "AK") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 5, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "AK mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangle = EPA monitor",
         fill = "Ambient PM", size = "Ambient PM") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 6)
ak_plot
```

@@

wmt_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "WMT") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    theme_void() +
    labs(title = "WMT mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations",
         fill = "Ambient temp", size = "Ambient temp") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 20)
wmt_plot
```

```{r}
nn_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "NN") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "NN mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations",
         fill = "Ambient temp", size = "Ambient temp") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 45)
nn_plot
```

```{r}
ak_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "AK") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 5, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "AK mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations",
         fill = "Ambient temp", size = "Ambient temp") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 30)
ak_plot
```

### 2020-04-03 exposure_initial_analysis.Rmd
analysis updates

---
title: "KidsAIR: initial exposure analysis"
author: "Ethan Walker"
date: "Started 2 Feb 2020, Updated 30 March 2020"
output: pdf_document
---

@@

>>>>

---
title: "KidsAIR: initial exposure analysis"
author: "Ethan Walker"
date: "Started 2 Feb 2020, Updated 3 April 2020"
output: pdf_document
---

@@

# Ambient temp/PM - by sampling date
```{r}
analysis_data <- exposure_analysis_data_long %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  #filter(area == "AK") %>% 
  filter(!is.na(sampling_day)) %>% 
  filter(!is.na(sample_date)) %>%
  select(area, home, child_id_char, sample_date, sampling_day, pm_mean_daily,
         zip:mean_temp_roll_4day) %>% 
  mutate(amb_pm_5 = amb_pm_24hr/5,
         mean_temp_5 = mean_temp/5,
         mean_temp_cat = cut(mean_temp, breaks = c(0, 30, 150),
                           labels = c("<30", "30+"),
                                 right = FALSE),
         amb_pm_cat = cut(amb_pm_24hr, breaks = c(0, 7, 100),
                           labels = c("<7", "7+"),
                                 right = FALSE))

median(analysis_data$amb_pm_24hr, na.rm = TRUE)
table(analysis_data$amb_pm_cat)

# Variables to use:
## amb_pm_5, amb_pm_cat,
## amb_pm_24hr, amb_pm_24hr_lag1, amb_pm_24hr_lag2, amb_pm_24hr_lag3
## amb_pm_roll_mean_2day, amb_pm_roll_mean_3day, amb_pm_roll_mean_4day
## mean_temp_5, mean_temp_cat,
## mean_temp, mean_temp_lag1, mean_temp_lag2, mean_temp_lag3
## mean_temp_roll_2day, mean_temp_roll_3day, mean_temp_roll_4day

cor.test(analysis_data$mean_temp, analysis_data$pm_mean_daily, method = "spearman")
pm_ambient_model <- lmer(log(pm_mean_daily) ~ amb_pm_cat + (1 | home), 
                      data = analysis_data)
pm_ambient_model <- lmer(pm_mean_daily ~ amb_pm_cat + (1 | home), 
                      data = analysis_data)

#summary(pm_ambient_model)
tidy(pm_ambient_model)
exp((-0.06723228)-1)*100
plot(pm_ambient_model, 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(pm_ambient_model), main = "QQ Plot")

pm_sums_plot <- analysis_data %>% 
  ggplot() + 
    geom_point(aes(log(pm_mean_daily), mean_temp)) +
    geom_smooth(aes(log(pm_mean_daily), mean_temp)) +
    theme_minimal()
pm_sums_plot
```
